---
title: "On the L1-acquisition of discourse like - Part 5: Reliability"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  word_document
bibliography: bibliography.bib
link-citations: yes
---

This document focuses on evaluating the reliability of the manual coding of the functions of dm like.


In a first step, we prepare the session by cleaning the workspace, loading packages, setting options, and defining paths.

```{r likeac_5_01}
# load packages
library(tidyverse)
library(here)
library(readxl)
library(flextable)
library(irr)
```

# Extarct examples for manual coding

Extract sample and save it to disc

```{r likeac_5_03, eval = F}
set.seed(20200810)
dmlike_sample <- base::readRDS(here::here("data", "dmlike_all_coded.rda")) %>%
  sample_n(200) %>%
  select(-LexicalIndecision, -Specification, -Modification, -Repair, -File, -Function, -DiscourseLike,
  -Speaker, -Example_long, -Speaker_long, -CleanedUtterance_long)
# inspect
head(dmlike_sample)
```

Save sample to disc

```{r likeac_5_05, eval = F}
# save 
base::saveRDS(dmlike_sample, file = here::here("data", "dmlike_reliability_sample.rda"))
```

# Evaluation of manual coding

```{r likeac_5_07}
# load data
man_01 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_LC.xlsx"), sheet = 1)
man_02 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_EA.xlsx"), sheet = 1)
man_03 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_JW.xlsx"), sheet = 1)
man_04 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_NW.xlsx"), sheet = 1)
man_05 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_KH.xlsx"), sheet = 1)
man_06 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_RR.xlsx"), sheet = 1)
man_07 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_AP.xlsx"), sheet = 1)
man_08 <- read_excel(here::here("reliability", "dmlike_reliabilitytesting_NM.xlsx"), sheet = 1)
cntl <- read.table(here::here("datatables", "dmlike_all_coded_orig.txt"), sep = "\t", header=TRUE, quote = "", skipNul = T) 
# inspect data
head(man_01)
```


```{r likeac_5_09}
# process and combine data
man_01 <- man_01 %>%
  dplyr::select(Function, ID) %>%
  mutate(Function = tolower(Function),
         Coder = "A01")
man_02 <- man_02 %>%
  dplyr::select(Function, ID) %>%
  mutate(Function = ifelse(Function == "1", "attention", 
                           ifelse(Function == "2", "cognitive",
                                  ifelse(Function == "3", "repair",
                                         ifelse(Function == "4", "specification", Function)))),
         Function = tolower(Function),
         Coder = "A02")
man_03 <- man_03 %>%
  dplyr::select(Function, ID) %>%
  mutate(Function = tolower(Function),
         Coder = "A03")
man_04 <- man_04 %>%
  dplyr::select(Function, ID) %>%
  mutate(Function = tolower(Function),
         Coder = "A04")
man_05 <- man_05 %>%
  dplyr::select(Function, ID) %>%
  mutate(Function = tolower(Function),
         Coder = "A05")
man_06 <- man_06 %>%
  dplyr::select(Function, ID) %>%
  mutate(Coder = "A06")
man_07 <- man_07 %>%
  dplyr::select(Function, ID) %>%
  mutate(Coder = "A07")
man_08 <- man_08 %>%
  dplyr::select(Function, ID) %>%
  mutate(Coder = "A08")
# extract item identifiers
idx <- man_01$ID
# extract control
cntl <- cntl %>%
  dplyr::select(ID, Specification, Modification, Repair, LexicalIndecision) %>%
  filter(ID %in% idx) %>%
  mutate(Coder = "Aut",
         Function = ifelse(Specification == 1, "specification",
                           ifelse(Modification == 1, "attention",
                                  ifelse(LexicalIndecision == 1, "cognitive",
                                         ifelse(Repair == 1, "repair", NA))))) %>%
  dplyr::select(ID, Coder, Function)
# combine data
man <- rbind(man_01, man_02, man_03, man_04, man_05, man_06, man_07, man_08, cntl) %>%
  mutate(Function = factor(Function)) %>%
  spread(Coder, Function)
# inspect data
head(man)
```

Test

```{r, eval = F}
test <- apply(man[, 2:ncol(man)],1,function(x) names(which.max(table(x))))
head(test)
```


# Evaluating reliability

We use Light's kappa [see @light1971measures or @conger1980integration] to evaluate the inter-rater reliability. Light's kappa is based on Cohen's kappa. @cohen1960coefficient suggested the following interpretation for kappa:

```{r, echo = F}
ValueOfKappa <- c(".0–.20", ".21–.40", ".41–.60", ".61–.80", ".81–1.0")
LevelOfAgreement <- c("None to slight", "Fair", "Moderate", "Substantial", "Almost Perfect")	
df <- data.frame(ValueOfKappa, LevelOfAgreement)
ft <- flextable(df)
ft
```

@mchugh2012reliability introduced a more rigorous interpretation that should be applied in medical studies (see below).

```{r, echo = F}
ValueOfKappa <- c(".0–.20", ".21–.39", ".40–.59", ".60–.79", ".80–.90", "Above.90")
LevelOfAgreement <- c("None", "Minimal", "Weak", "Moderate", "Strong", "Almost Perfect")	
PercentOfDataReliable <- c("0–4%", "4–15%", "15–35%", "35–63%", "64–81%", "82–100%")
df <- data.frame(ValueOfKappa, LevelOfAgreement, PercentOfDataReliable)
ft <- flextable(df)
ft
```




```{r kappa}
# activate packages
library(irr)
# extract reliability measures
reliability <- kappam.light(man[, 3:10])
# inspect results
reliability
```




```{r alpha}
# activate packages
library(ltm)
# extract reliability measures
cronalpha <- ltm::cronbach.alpha(as.data.frame(man[, 3:10]))
# inspect results
cronalpha
```

# Check author's against coders calssification


```{r overlap}
coders <- apply(man[, 3:9],1,function(x) names(which.max(table(x))))
author <- man[,10]
man$Check <- as.vector(coders == author)
# inspect data
head(man)
```

Check percentage of deviation

```{r overlap}
table(man$Check)
# percent deviation
round(table(man$Check)[1]/sum(table(man$Check))*100, 2)


```

Create table to combine with data

```{r extract}
# extract functions
Function <- apply(man[, 2:ncol(man)],1,function(x) names(which.max(table(x))))
NFunction <- str_to_title(Function)
# extract identifiers
ID <- man$ID
# combine fun + id to df
funtb <- data.frame(ID, NFunction)
# inspect df
head(funtb)
```

Add coders classification to data


```{r combine}
# load data
dmlike_new <- read.table(here::here("datatables", "dmlike_all_coded.txt"), sep = "\t", header=TRUE, quote = "", skipNul = T) 
dmlike_new <- left_join(dmlike_new, funtb, by = "ID")
# inspect data
head(dmlike_new)
```

Clean combined data

```{r clean}
dmlike_new <- dmlike_new %>%
  dplyr::mutate(Function_Fine = Function,
                Function = ifelse(is.na(NFunction), Function, NFunction),
                Function = case_when(Function == "Emphasizing" ~ "Attention",
                                     Function == "FocusMarker" ~ "Attention",
                                     Function == "Hedge" ~ "Attention",
                                     Function == "LexicalIndecision" ~ "Cognitive",
                                     Function == "Modifier" ~ "Attention",
                                     Function == "RepairIndicator" ~ "Repair",
                                     Function == "RestartSignal" ~ "Repair",
                                     Function == "Specification" ~ "Specification",
                                     TRUE ~ Function)) %>%
  dplyr::mutate(Specification = ifelse(Function == "Specification", 1, 0),
                Attention = ifelse(Function == "Attention", 1, 0),
                Cognitive = ifelse(Function == "Cognitive", 1, 0),
                Specification = ifelse(Function == "Specification", 1, 0)) %>%
  dplyr::mutate(Function = factor(Function),
                Interlocutor = factor(Interlocutor)) %>%
  dplyr::select(-NFunction)
# save data
write.table(dmlike_new, here::here("datatables", "dmlike_all_coded_new.txt"), sep = "\t", row.names = F, quote = F)
# inspect data
head(dmlike_new)
```

## Extract session information

```{r}
sessionInfo()
```

***

The END

***

