---
title: "On the L1-acquisition of discourse like - Part 2"
author: "Anonymous"
date: "`r format(Sys.time(), '%Y-%m-%d')`"
output:
  bookdown::html_document2: default
bibliography: bibliography.bib
link-citations: yes
---

This document shows an analysis that was performed with the aim of investigating the acquiasition of discourse *like* in American English based on data from the *Child Language Data Exchange System* (CHILDES). The following represents part 2 of this analysis.

# Prepare session 

* cleaning workspace
* loading packages
* setting options
* defining paths

```{r likeac_2_01}
# load packages
library(tidyverse)
library(plyr)
library(reshape)
library(here)
```

We now read in the data and combine the by-instance data with the bio-demographic information.

```{r likeac_2_02}
# read in data
bio <- base::readRDS(here::here("data", "HSDDLbiodemographicsbiowc.rda"))
dmlike <- base::readRDS(here::here("data", "dmlike_all_coded.rda"))
# remove na
dmlike <- dmlike %>%
  na.omit() %>%
  dplyr::filter(DiscourseLike == 1)  %>%
  dplyr::select(-Interlocutor)
# create formality column
informal <- c("Toy play", "Meal time", "Elicited report")
rmspeakers <- c("Peer", "Other")
bio <- bio %>%
  dplyr::rename(Situation = SituationType) %>%
  dplyr::mutate(SituationType = dplyr::case_when(Situation %in% informal ~ "informal", 
                                                 TRUE ~ "formal")) %>%
  # repair missing gender information
  dplyr::mutate(Gender = dplyr::case_when(File == "HV1/MT/trumt1" & Speaker == "CHI" ~ "male", 
                                          File == "HV1/ER/bober1" & Speaker == "CHI" ~ "male",
                                          File == "HV2/BR/todbr2" & Speaker == "CHI" ~ "male", 
                                          File == "HV2/TP/castp2" & Speaker == "CHI" ~ "male", 
                                          File == "HV1/MT/brtmt1" & Speaker == "CHI" ~ "female", 
                                          File == "HV2/BR/jesbr2" & Speaker == "CHI" ~ "female", 
                                          TRUE ~ Gender)) %>%
  # create age columns
  dplyr::mutate(Cohort = dplyr::case_when(AgeCategory == 3 ~ "3-4",
                                          AgeCategory == 4 ~ "3-4",
                                          AgeCategory == 5 ~ "5-6",
                                          AgeCategory == 6 ~ "5-6",
                                          AgeCategory == 7 ~ "7-8",
                                          AgeCategory == 8 ~ "7-8",
                                          AgeCategory == 9 ~ "9-10",
                                          AgeCategory == 10 ~ "9-10",
                                          AgeCategory == 11 ~ "11-12",
                                          AgeCategory == 12 ~ "11-12",
                                          TRUE ~ as.character(AgeCategory)))
# combine data like data with bio-demographic data
like <- dplyr::left_join(dmlike, bio, by = c("File", "Speaker"))
# inspect data
head(like)
```

In addition, we add the like data to the bio-demographic data.

```{r likeac_2_03}
# condense dmlike
sumlike <- dmlike %>%
  dplyr::select(File, Speaker, DiscourseLike, Attention,
                Repair, Cognitive, Specification) %>%
  dplyr::group_by(File, Speaker) %>%
  dplyr::summarise(DiscourseLike = sum(DiscourseLike), 
                   Attention = sum(Attention),
                   Repair = sum(Repair), 
                   Cognitive = sum(Cognitive), 
                   Specification = sum(Specification))
speakers <- dplyr::left_join(bio, sumlike, by = c("File", "Speaker")) %>%
  dplyr::mutate(DiscourseLike = DiscourseLike %>% replace_na(0),
                Attention = Attention %>% replace_na(0),
                Repair = Repair %>% replace_na(0),
                Cognitive = Cognitive %>% replace_na(0),
                Specification = Specification %>% replace_na(0)) %>%
  # repair gender
  dplyr::mutate(Child = str_remove_all(File, ".*/"),
                Child = str_sub(Child, 1, 3)) %>%
  dplyr::mutate(Gender = case_when(Child == "ali" & Speaker == "CHI" ~ "female",
                                   Child == "gil" & Speaker == "CHI" ~ "male",
                                   Child == "zan" & Speaker == "CHI" ~ "male",
                                   TRUE ~ Gender)) %>%
  dplyr::select(-Child)
# inspect data
head(speakers)
```

```{r testing}
test01 <- speakers %>%
  dplyr::select(File, Speaker, DiscourseLike) %>%
  dplyr::group_by(Speaker) %>%
  dplyr::summarise(DiscourseLike = sum(DiscourseLike)) %>%
  dplyr::filter(Speaker == "CHI" | Speaker == "MOT" | Speaker == "FAT")
test01
```




We will now use the data sets produced above to create visualizations

```{r likeac_2_04}
pd1 <- speakers %>%
  dplyr::select(WordCount, Locutor, Situation, AgeCategory) %>%
  dplyr::rename(Speaker = Locutor, Age = AgeCategory) %>%
  dplyr::filter(Speaker == "Child") %>%
  dplyr::group_by(Situation, Age) %>%
  dplyr::summarise(Words = sum(WordCount)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(Situation) %>%
  dplyr::mutate(Percent = round(Words/sum(Words)*100, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Age = factor(Age),
                Situation = factor(Situation))
# inspect data
pd1
```

```{r likeac_2_05}
ggplot(pd1, aes(Age, Words)) + 
  facet_wrap(pd1$Situation, nrow = 4) + 
  geom_bar(stat="identity") + #, position = position_dodge()) +
  scale_fill_manual(values=c("gray20")) + 
  geom_text(aes(label=paste(round(Words/1000,1), "\n(", round(Percent, 1), ")", 
                            sep = "")), 
            color="black", y = pd1$Words+10000, size=2.5) +
  theme_set(theme_bw(base_size = 12)) +   
  theme(legend.position="top", legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Age of Child",y = "Words (N)") +
  coord_cartesian(ylim = c(0, 50000)) +
  scale_y_continuous(breaks=seq(0, 60000, 10000))
ggsave(file = here::here("images", "Fig8.png"),
         width = 15,  height = 20, units = c("cm"),  dpi = 320)
```



```{r likeac_2_07a}
pd3 <- speakers %>%
  dplyr::select(WordCount, Locutor, SituationType, Cohort) %>%
  dplyr::filter(Cohort != "11-12") %>%
  dplyr::rename(Speaker = Locutor, Age = Cohort, Situation = SituationType) %>%
  dplyr::group_by(Situation, Speaker, Age) %>%
  dplyr::summarise(Words = sum(WordCount)) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(Situation, Age) %>%
  dplyr::mutate(Percent = round(Words/sum(Words)*100, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Age = factor(Age),
                Situation = factor(Situation))
# inspect data
pd3
```

```{r likeac_2_07b}
ggplot(pd3, aes(Age, Words, fill = Speaker)) + 
  facet_wrap(pd3$Situation, nrow = 2) + 
  geom_bar(stat="identity", position = position_dodge()) +
  scale_fill_manual(values=c("gray20", "gray40", "gray60", "gray80")) + 
  geom_text(aes(label=Percent), color="black", position = position_dodge(.9), 
                vjust=-1.2, size=3) +
  theme_set(theme_bw(base_size = 12)) +   
  theme(legend.position="top", legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Age",y = "Words (N)") +
  coord_cartesian(ylim = c(0, 300000)) +
  scale_y_continuous(breaks=seq(0, 300000, 50000))
ggsave(file = here::here("images", "WordsCohortSituationType.png"),
         width = 25,  height = 10, units = c("cm"),  dpi = 320)
```

We now remove speakers older than 10 and speakers other than children and primary caregiver from the sepakers-data set.

```{r likeac_2_08}
Table1 <- speakers %>%
  dplyr::select(Locutor, SituationType, Cohort, WordCount, DiscourseLike) %>%
  dplyr::group_by(Locutor, SituationType, Cohort) %>%
  dplyr::summarise(Words = sum(WordCount),
                   Like = sum(DiscourseLike)) %>%
  dplyr::mutate(Frequency = round(Like/Words*1000, 2)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Locutor = factor(Locutor),
                SituationType = factor(SituationType),
                Cohort = factor(Cohort)) 
write.table(Table1, file = here::here("datatables", "Table1.txt"), 
            row.names = FALSE, col.names = TRUE, quote = F)
# inspect data
Table1
```

```{r likeac_2_09}
nrow(speakers)
speakers <- speakers %>%
  dplyr::select(-OriginalAge, -SocioEconomicStatus) %>%
  dplyr::filter(Cohort != "11-12",
                Locutor != "Other",
                Locutor != "Peer") %>%
  na.omit()# inspect data
nrow(speakers)
```



```{r likeac_2_09}
speakers <- speakers %>%
  dplyr::ungroup() %>%
  # collapsing MOT and FAT
  dplyr::select(-Speaker, -DateOfBirth, -DateOfRecording, -Participants, -Visit) %>%
  dplyr::mutate(Gender = ifelse(Locutor == "Child", Gender, "unknown")) %>%
  dplyr::group_by(File, Locutor) %>%
  dplyr::summarise(Age = names(table(Age)),
                   SituationType = names(table(SituationType)),
                   Situation = names(table(Situation)),
                   Cohort = names(table(Cohort)),
                   AgeCategory = names(table(AgeCategory)),
                   Gender = names(table(Gender)),
                   DiscourseLike = sum(DiscourseLike),
                   Attention = sum(Attention), 
                   Repair = sum(Repair), 
                   Cognitive = sum(Cognitive), 
                   Specification = sum(Specification),
                   WordCount = sum(WordCount)) %>%
  dplyr::mutate(Cohort = factor(Cohort),
                Locutor = factor(Locutor),
                SituationType = factor(SituationType),
                Age = as.numeric(Age),
                AgeCategory = factor(AgeCategory),
                Situation = factor(Situation),
                Gender = factor(Gender))
# save
base::saveRDS(speakers, file = here::here("data", "speakers.rda"))
# inspect data
nrow(speakers);head(speakers)
``` 

We exclude the same data from the like-data set.

```{r likeac_2_10}
nrow(like)
like <- like %>%
  dplyr::select(-OriginalAge, -SocioEconomicStatus) %>%
  dplyr::filter(Cohort != "11-12",
                Locutor != "Other",
                Locutor != "Peer") %>%
  na.omit()
nrow(like)
``` 

```{r testing}
test02 <- speakers %>%
  dplyr::select(Locutor, DiscourseLike) %>%
  dplyr::group_by(Locutor) %>%
  dplyr::summarise(DiscourseLike = sum(DiscourseLike))
test02
```


```{r testing}
test03 <- like %>%
  dplyr::select(Locutor, DiscourseLike) %>%
  dplyr::group_by(Locutor) %>%
  dplyr::summarise(DiscourseLike = sum(DiscourseLike))
test03
```


```{r likeac_2_11a}
pd4 <- speakers %>%
  dplyr::select(WordCount, Locutor, SituationType, Cohort) %>%
  dplyr::filter(Cohort != "11-12") %>%
  dplyr::rename(Speaker = Locutor, Age = Cohort, Situation = SituationType) %>%
  dplyr::group_by(Situation, Speaker, Age) %>%
  dplyr::summarise(Words = sum(WordCount)) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(Situation, Age) %>%
  dplyr::mutate(Percent = round(Words/sum(Words)*100, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Age = factor(Age),
                Situation = factor(Situation))
# inspect data
pd4
```



```{r likeac_2_11b}
ggplot(pd4, aes(Age, Words, fill = Speaker)) + 
  facet_wrap(pd4$Situation, nrow = 2) + 
  geom_bar(stat="identity", position = position_dodge()) +
  scale_fill_manual(values=c("gray20", "gray60")) + 
  geom_text(aes(label=paste(round(Words/1000, 1), "\n(", round(Percent, 1), "%)", sep = "")),
            color="black", position = position_dodge(.9), vjust=-.5, size=3) +
  theme_set(theme_bw(base_size = 12)) +   
  theme(legend.position="top", legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Age of Child",y = "Words (in 1,000s)") +
  coord_cartesian(ylim = c(0, 400000)) +
  scale_y_continuous(breaks=seq(0, 400000, 100000), labels = seq(0, 400, 100))
ggsave(file = here::here("images", "Fig1.png"),
         width = 15,  height = 10, units = c("cm"),  dpi = 320)
```

```{r likeac_2_12a}
Table2 <- speakers %>%
  dplyr::select(File, Locutor, SituationType, Cohort, 
                WordCount, DiscourseLike) %>%
  dplyr::mutate(SpeakerID = str_replace_all(File, ".*/", "")) %>%
  dplyr::mutate(SpeakerID = substr(SpeakerID, 1, 3)) %>%
  dplyr::mutate(SpeakerID = paste(SpeakerID, Locutor, sep = "")) %>%
  dplyr::mutate(SpeakerID = factor(SpeakerID)) %>%
  dplyr::select(-File) %>%
  dplyr::group_by(Locutor, SituationType, Cohort, SpeakerID) %>%
  dplyr::summarise(Words = sum(WordCount),
                   Like = sum(DiscourseLike),
                   Speakers = n()) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(Locutor, SituationType, Cohort) %>%
  dplyr::summarise(Words = sum(Words),
                   Like = sum(Like),
                   Speakers = n()) %>%
  dplyr::mutate(Frequency = round(Like/Words*1000, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Locutor = factor(Locutor),
                SituationType = factor(SituationType),
                Cohort = factor(Cohort)) 
write.table(Table2, file = here::here("datatables", "Table2.txt"), 
            row.names = FALSE, col.names = TRUE, quote = F)
# inspect data
Table2
```

```{r likeac_2_12b}
Table3 <- speakers %>%
  dplyr::select(File,  Locutor, Gender, SituationType, Cohort, 
                WordCount, DiscourseLike) %>%
  dplyr::mutate(SpeakerID = str_replace_all(File, ".*/", "")) %>%
  dplyr::mutate(SpeakerID = substr(SpeakerID, 1, 3)) %>%
  dplyr::mutate(SpeakerID = paste(SpeakerID, Locutor, sep = "")) %>%
  dplyr::mutate(SpeakerID = factor(SpeakerID)) %>%
  dplyr::select(-File) %>%
  dplyr::group_by(Cohort, Locutor, SituationType, Gender, SpeakerID) %>%
  dplyr::summarise(Words = sum(WordCount),
                   Like = sum(DiscourseLike),
                   Speakers = n()) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(Cohort, Locutor, SituationType, Gender) %>%
  dplyr::summarise(Words = sum(Words),
                   Like = sum(Like),
                   Speakers = n()) %>%
  dplyr::mutate(Frequency = round(Like/Words*1000, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Locutor = factor(Locutor),
                SituationType = factor(SituationType),
                Cohort = factor(Cohort)) 
write.table(Table3, file = here::here("datatables", "Table3.txt"), 
            row.names = FALSE, col.names = TRUE, quote = F)
# inspect data
Table3
```

```{r likeac_2_12c}
Table4 <- speakers %>%
  dplyr::select(File, Locutor, Gender, SituationType, Cohort, 
                WordCount, DiscourseLike, Attention, Repair,
                Cognitive, Specification) %>%
  dplyr::mutate(SpeakerID = str_replace_all(File, ".*/", "")) %>%
  dplyr::mutate(SpeakerID = substr(SpeakerID, 1, 3)) %>%
  dplyr::mutate(SpeakerID = paste0(SpeakerID, Locutor)) %>%
  dplyr::mutate(SpeakerID = factor(SpeakerID)) %>%
  dplyr::select(-File) %>%
  dplyr::group_by(Cohort, Locutor, SituationType, Gender, SpeakerID) %>%
  dplyr::summarise(Words = sum(WordCount),
                   Like = sum(DiscourseLike),
                   Attention = sum(Attention), 
                   Repair = sum(Repair),
                   Cognitive = sum(Cognitive),
                   Specification = sum(Specification),
                   Speakers = n()) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(Cohort, Locutor, SituationType, Gender) %>%
  dplyr::summarise(Words = sum(Words),
                   Like = sum(Like),
                   Attention = sum(Attention), 
                   Repair = sum(Repair),
                   Cognitive = sum(Cognitive),
                   Specification = sum(Specification),
                   Speakers = n()) %>%
  dplyr::mutate(Freq_Like = round(Like/Words*1000, 2)) %>%
  dplyr::mutate(Pcnt_Att = round(Attention/Like*100, 1)) %>%
  dplyr::mutate(Pcnt_Rep = round(Repair/Like*100, 1)) %>%
  dplyr::mutate(Pcnt_Cog = round(Cognitive/Like*100, 1)) %>%
  dplyr::mutate(Pcnt_Spe = round(Specification/Like*100, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Like = paste(Like, " (", Freq_Like, ")", sep = "")) %>%
  dplyr::mutate(Attention = paste(Attention, " (", Pcnt_Att, ")", 
                                     sep = "")) %>%
  dplyr::mutate(Repair = paste(Repair, " (", Pcnt_Rep, ")", sep = "")) %>%
  dplyr::mutate(Cognitive = paste(Cognitive, " (", Pcnt_Cog, ")",
                                          sep = "")) %>%
  dplyr::mutate(Specification = paste(Specification, " (", Pcnt_Spe, ")", 
                                      sep = "")) %>% 
  dplyr::select(-Freq_Like, -Pcnt_Att, -Pcnt_Rep, -Pcnt_Cog, -Pcnt_Spe) %>%
  dplyr::mutate(Locutor = factor(Locutor),
                SituationType = factor(SituationType),
                Cohort = factor(Cohort)) 
write.table(Table4, file = here::here("datatables", "Table4.txt"), 
            row.names = FALSE, col.names = TRUE, quote = F)
# inspect data
Table4
```

```{r likeac_2_14a}
pd6 <- speakers %>%
  dplyr::select(Cohort, DiscourseLike, Locutor, SituationType, WordCount) %>%
  dplyr::group_by(Cohort, Locutor, SituationType) %>%
  dplyr::mutate(Frequency = round(DiscourseLike/WordCount*1000, 2))
# inspect data
pd6
```

```{r likeac_2_14b}
ggplot(pd6, aes(Cohort, Frequency, colour = SituationType)) +
  stat_summary(fun.y = mean, geom = "point") +
  stat_summary(fun.y = mean, geom = "point", aes(group = SituationType)) +
  stat_summary(fun.data = mean_cl_boot, geom = "errorbar", width = 0.2) +
  facet_wrap(~ Locutor, nrow = 1) +
  coord_cartesian(ylim = c(0, 5)) +
  theme_set(theme_bw(base_size = 15)) +
  labs(x = "Age of Child", y = "Frequency \n(per 1,000 words)", colour = "SituationType") +
  theme(legend.position="top",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.background = element_blank()) +
  scale_color_manual(values = c("gray30", "gray80"))
ggsave(file = here::here("images", "LikeAgeSituationSpeaker_errorbars.png"), 
         width = 20,  height = 10, units = c("cm"), dpi = 320)
```



## Extract examples

```{r likeac_2_15}
set.seed(2020012201)
chi <- like %>%
  dplyr::filter(Locutor == "Child")
examples <- like %>%
  dplyr::select(File, Example_long, Locutor, Function) %>%
  dplyr::filter(Locutor == "Child") %>%
  dplyr::sample_n(nrow(chi)) %>%
  dplyr::arrange(Function) %>%
  dplyr::select(-Locutor)
# save examples
write.table(examples, file = here::here("datatables", "examples.txt"), 
            row.names = FALSE, col.names = TRUE, quote = F)
# inspect examples
head(examples)
```

## Bar plot

Functions by age, locutor, and situation type


```{r likeac_2_18a}
pd8 <- like %>%
  dplyr::select(SituationType, Function, Locutor, Cohort, DiscourseLike) %>%
  dplyr::mutate(DiscourseLike = rep(1, nrow(like))) %>%
  dplyr::rename(Speaker = Locutor, Age = Cohort, Situation = SituationType) %>%
  dplyr::group_by(Situation, Speaker, Age, Function) %>%
  dplyr::summarise(Likes = sum(DiscourseLike)) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(Situation, Speaker, Age) %>%
  dplyr::mutate(Percent = round(Likes/sum(Likes)*100, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Function = ifelse(Function == "LexicalIndecision", "Cognitive", Function)) %>%
  dplyr::mutate(Age = factor(Age),
                Function = factor(Function),
                Speaker = factor(Speaker),
                Situation = factor(Situation))
# inspect data
pd8
```

```{r likeac_2_18b}
ggplot(pd8, aes(Age, Percent, fill = Function)) + 
  facet_grid(Speaker ~ Situation) + 
  geom_bar(stat="identity", position = position_dodge()) +
  scale_fill_manual(values=c("gray20", "gray40", "gray60", "gray80")) +
  geom_text(aes(label=paste(round(Percent, 1), "\n(", Likes, ")", sep = "")),
            color="black", position = position_dodge(.9), vjust=-.5, size=3) +
  theme_set(theme_bw(base_size = 15)) +   
  theme(legend.position="top", legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Age of Child",y = "Percent") +
  coord_cartesian(ylim = c(0, 100)) +
  scale_y_continuous(breaks=seq(0, 100, 20))
ggsave(file = here::here("images", "LikeCohortSituationSpeaker_bar.png"), 
         width = 25,  height = 15, units = c("cm"), dpi = 320)
```

```{r likeac_2_21a}
Agelbs <- names(table(speakers$Cohort))
pd9 <- like %>%
  dplyr::select(SituationType, Function, Locutor, Cohort, DiscourseLike) %>%
  dplyr::mutate(DiscourseLike = rep(1, nrow(like))) %>%
  dplyr::mutate(Cohort = ifelse(Cohort == "3-4", 1, 
                         ifelse(Cohort == "5-6", 2,
                         ifelse(Cohort == "7-8", 3,
                         ifelse(Cohort == "9-10", 4, Cohort))))) %>%
  dplyr::rename(Speaker = Locutor, Age = Cohort, Situation = SituationType) %>%
  dplyr::group_by(Situation, Speaker, Age, Function) %>%
  dplyr::summarise(Likes = sum(DiscourseLike)) %>%
    dplyr::ungroup() %>%
    dplyr::group_by(Situation, Speaker, Age) %>%
  dplyr::mutate(Percent = round(Likes/sum(Likes)*100, 1)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Age = as.numeric(Age),
                Function = factor(Function),
                Speaker = factor(Speaker),
                Situation = factor(Situation))
# inspect data
pd9
```



```{r likeac_2_21b}
ggplot(pd9, aes(Age, Percent, linetype = Function, color = Function)) + 
  facet_grid(Speaker ~ Situation) + 
  geom_line(size = 1) +
    scale_linetype_manual(values=c("solid", "dashed", "dotdash", "dotted"), 
                        name=c(""),
                        breaks = c("Attention", "Cognitive", 
                                   "Repair", "Specification"),
                        labels = c("Attention","Cognitive", 
                                   "Repair", "Specification")) +
  scale_color_manual(values=c("gray20", "gray40", "gray60", "gray80"), 
                        name=c(""),
                        breaks = c("Attention", "Cognitive", 
                                   "Repair", "Specification"),
                        labels = c("Attention", "Cognitive", 
                                   "Repair", "Specification")) +
  theme_set(theme_bw(base_size = 15)) +   
  theme(legend.position="top", legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Age of Child",y = "Percent") +
  coord_cartesian(ylim = c(0, 100)) +
  scale_y_continuous(breaks=seq(0, 100, 20)) +
    scale_x_continuous(name = "Age of Child",
                     breaks = c(1, 2, 3, 4),
                     labels=Agelbs)
ggsave(file = here::here("images", "LikeFunctionCohortSituationSpeaker_line.png"), 
         width = 25,  height = 15, units = c("cm"), dpi = 320)
```

```{r likeac_2_21c}
pd10 <- speakers %>%
  dplyr::select(SituationType, Attention, Repair, Cognitive,
                Specification, Locutor, Cohort, WordCount) %>%
  tidyr::gather(key = "Function", value = "Frequency", "Attention":"Specification") %>%
  dplyr::rename(Speaker = Locutor, Age = Cohort, 
                Situation = SituationType, Words = WordCount) %>%
  dplyr::group_by(Situation, Speaker, Function, Age) %>%
  dplyr::summarise(Likes = sum(Frequency),
                   Words = sum(Words)) %>%
  dplyr::mutate(RelativeFrequency = round(Likes/Words*1000, 2)) %>%
  dplyr::ungroup() %>%
  dplyr::mutate(Age = factor(Age),
                Function = factor(Function),
                Speaker = factor(Speaker),
                Situation = factor(Situation))
# inspect data
pd10
```

```{r likeac_2_21d}
ggplot(pd10, aes(Age, RelativeFrequency, fill = Function)) + 
  facet_grid(Speaker ~ Situation) + 
  geom_bar(stat="identity", position = position_dodge()) +
  scale_fill_manual(values=c("gray20", "gray40", "gray60", "gray80")) +
  geom_text(aes(label=paste(RelativeFrequency, "\n(", Likes, ")", sep = "")),
            color="black", position = position_dodge(.9), vjust=-.5, size=3) +
  theme_set(theme_bw(base_size = 15)) +   
  theme(legend.position="top", legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Age of Child",y = "Frequency\n(per 1,000 words)") +
  coord_cartesian(ylim = c(0, 3)) +
  scale_y_continuous(breaks=seq(0, 3, 1))
ggsave(file = here::here("images", "LikeRelFreqCohortSituationSpeaker_bar.png"), 
         width = 30,  height = 15, units = c("cm"), dpi = 320)
```


```{r likeac_2_21e}
pd11 <- pd10 %>%
  dplyr::mutate(Age = ifelse(Age == "3-4", 1, 
                      ifelse(Age == "5-6", 2,
                      ifelse(Age == "7-8", 3,
                      ifelse(Age == "9-10", 4, Age))))) %>%
  dplyr::mutate(Age = as.numeric(Age))
# inspect data
head(pd11)
```



```{r likeac_2_21f}
ggplot(pd11, aes(jitter(Age), RelativeFrequency, linetype = Function, color = Function)) + 
  facet_grid(Speaker ~ Situation) + 
  geom_line(size = 1) +
    scale_linetype_manual(values=c("solid", "dashed", "dotdash", "dotted"), 
                        name=c(""),
                        breaks = c("Attention", "Cognitive", "Repair", "Specification"),
                        labels = c("Attention", "Cognitive", "Repair", "Specification")) +
  scale_color_manual(values=c("gray20", "gray40", "gray60", "gray80"), 
                        name=c(""),
                        breaks = c("Attention", "Cognitive", "Repair", "Specification"),
                        labels = c("Attention", "Cognitive", "Repair", "Specification")) +
  theme_set(theme_bw(base_size = 15)) +   
  theme(legend.position="top", legend.title = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  labs(x = "Age of Child",y = "Frequency\n(per 1,000 words)") +
  coord_cartesian(ylim = c(0, 3)) +
  scale_y_continuous(breaks=seq(0, 3, 1)) +
  scale_x_continuous(name = "Age of Child",
                     breaks = c(1, 2, 3, 4),
                     labels=Agelbs) 
ggsave(file = here::here("images", "LikeRelFreqFunctionCohortSituationSpeaker_line.png"), 
         width = 25,  height = 15, units = c("cm"), dpi = 320)
```

Now, we create the data set for the regression analysis.

```{r likeac_2_22a}
# create speaker for joining table
speaker_forjoining <- speakers %>%
  dplyr::select(File, Locutor, WordCount, SituationType, 
                DiscourseLike, Attention, Repair, Cognitive,
                Specification) %>%
  dplyr::filter(Locutor == "PrimaryCaregiver") %>%
  dplyr::group_by(File, Locutor) %>%
  dplyr::summarise(DiscourseLike = sum(DiscourseLike),
                   WordCount = sum(WordCount),
                   Attention = sum(Attention),
                   Repair = sum(Repair),
                   Cognitive = sum(Cognitive),
                   Specification = sum(Specification)) %>%
  dplyr::mutate(Like_Freq = round(DiscourseLike/WordCount*1000, 3),
                Att_Freq = round(Attention/WordCount*1000, 3), 
                Rep_Freq = round(Repair/WordCount*1000, 3),
                Cog_Freq = round(Cognitive/WordCount*1000, 3),
                Spe_Freq = round(Specification/WordCount*1000, 3)) %>%
  dplyr::ungroup() %>%
  dplyr::select(-Locutor, -DiscourseLike, -WordCount, -Attention, -Cognitive, -Repair, -Specification) %>%
  as.data.frame()
# create like for joining table
like_forjoining <- like %>%
  dplyr::select(File, Gender, Participants, Locutor, Visit, Age, 
  SituationType, Function, DiscourseLike) %>%
  dplyr::filter(Locutor == "Child") %>%
  dplyr::select(-Locutor) %>%
  as.data.frame()
# combine data
datalike <- dplyr::left_join(like_forjoining, speaker_forjoining, by = c("File")) %>%
  dplyr::rename(Child = File) %>%
  dplyr::mutate(Child = str_replace_all(Child, ".*/", "")) %>%
  dplyr::mutate(Child = str_sub(Child, 1, 3)) %>%
  # remove visit (collinear with Age)
  dplyr::select(-Visit) %>%
  # remove incomplete cases
  tidyr::replace_na(list(Like_Freq = 0, Att_Freq = 0, Rep_Freq = 0, Cog_Freq = 0, Spe_Freq = 0)) %>%
  na.omit()
# save 
base::saveRDS(datalike, file = here::here("data", "datadmlike.rda"))
# inspect data
head(datalike)
```

Check the percentage of children that have used discourse *like* in the data.

```{r likeac_2_22b}
likeusers <- speakers %>% 
  dplyr::select(DiscourseLike, Locutor, File) %>%
  dplyr::filter(Locutor == "Child") %>%
  dplyr::select(-Locutor) %>%
  dplyr::mutate(File = str_replace_all(File, ".*/", "")) %>%
  dplyr::mutate(File = str_sub(File, 1, 3)) %>%
  dplyr::group_by(File) %>%
  dplyr::summarise(User = sum(DiscourseLike)) %>%
  dplyr::mutate(User = ifelse(User >= 1, 1, User)) %>%
  dplyr::ungroup() %>%
  dplyr::group_by(User) %>%
  dplyr::summarise(LikeUser = n())
PercentLikeUsers <- round(likeusers$LikeUser[2]/sum(likeusers$LikeUser)*100, 1)
# inspect data
PercentLikeUsers
```

## Extract session information

```{r}
sessionInfo()
```


***

We have reached the end of Part 2 of the analysis.

***

